Security Properties for Stack Safety

### 2021-05-15 short/main.tex
Another try

Our threat model is very strong, allowing the attacker (i.e., the callee) to
execute arbitrary code, including code that might attempt to smash
the stack to disrupt the program's control flow.
Our stack safety properties demand that, even in the presence of such
attackers, confidentiality and integrity must
still apply to data in suspended stack frames.
% all of the data they would under more idealized conditions.
%This formulation not only captures the intuition
%that the callee cannot directly access the caller's state; it also gives a novel
%interpretation of integrity and confidentiality in the presence of control-flow
%attacks.
\bcp{I tried rewriting the first part of the paragraph, and I like it
  better, but now there's a big gap between that and what comes next.  I
  wonder whether we need to turn the next bit into a separate discussion of
  ``what it means to return''...  In any case, I felt like the previous
  version of the whole paragraph didn't quite nail what we needed to say
  about all this.}
The key is that every call has a corresponding predicate on states,
designated as the ``return target,''
which defines what it means for that call to truly return: the program counter
must be at the next instruction, and the stack pointer restored to its original
value. A callee may execute a return instruction,
but if it does not reach a return target we simply do not recognize it as a return.
So the callee can be ``active'', and the caller protected, even if the callee is
executing instructions outside of its normal footprint.
% that don't look like they belong to the caller.

>>>>

Our threat model is very strong, allowing the attacker (i.e., the callee) to
execute arbitrary code, including code that might attempt to smash
the stack to disrupt the program's control flow.
Our stack safety properties demand that, even in the presence of such
attackers, confidentiality and integrity must
still apply to data in suspended stack frames until the callee returns.
% all of the data they would under more idealized conditions.
%This formulation not only captures the intuition
%that the callee cannot directly access the caller's state; it also gives a novel
%interpretation of integrity and confidentiality in the presence of control-flow
%attacks.
% \bcp{I tried rewriting the first part of the paragraph, and I like it
%   better, but now there's a big gap between that and what comes next.  I
%   wonder whether we need to turn the next bit into a separate discussion of
%   ``what it means to return''...  In any case, I felt like the previous
%   version of the whole paragraph didn't quite nail what we needed to say
%   about all this.}
% \sna{Better transition.}
The question then arises: when, exactly, are suspended frames
reactivated---or equivalently,
what constitutes a return in this setting? It is not obvious, since our
setting is a concrete, low-level ISA where the same opcode might sometimes
be used to return from a call and sometimes for other purposes.
Our solution is to associate with each call a corresponding predicate on states,
its ``return target,''
which defines what it means for that call to truly return: the program counter
must be at the next instruction, and the stack pointer restored to its original
value. A callee may execute a return instruction,
but if it does not reach a return target we simply do not recognize it as a
return.
So the callee can be ``active'', and the caller protected, even if the callee is
executing instructions outside of its normal footprint.  \bcp{I tried
  another rewrite of the end of the paragraph.  I think it's getting there,
  but it's probably now a bit too long as well as too detailed.}
